Parsing Tweets into Universal Dependencies

### 2017-09-22 paper.tex
sync

\newcommand{\yjcomment}[1]{\textcolor{orange}{[$_\mathrm{L}^\mathrm{Y}$\textsc{#1}]}}
\newcommand{\nascomment}[1]{\textcolor{blue}{[#1 ---\textsc{nas}]}}

@@

\section{Introduction}
Analyzing the syntax of tweets is challenging for traditional NLP tools because most of the tweet texts are informal and noisy.

In this paper, we propose to parse the tweets in the convention of
universal dependencies and built up the whole pipeline to parse the
tweets from the raw text form.

Motivation notes:  explain why UD is attractive (and more attractive
than what previous work used, which was based on YM).  one reason is
that it might allow sharing of texts annotated in different genres (or
even languages, cite Waleed).  but universal annotation schemes are
challenging!  this paper contends with the challenges of
applying UD to social media texts.

\nascomment{Points that were in older text that I want to keep around:}
\begin{itemize}
\item Despite the informal nature of tweets, we argue that they basically follow the same grammar as their formal language counterpart.
\item UD was designed to handle the variant syntactic phenomenons across different languages and we expect its `context head' principle will bring convenience to the parsing of informal and even ungrammatical tweets. 
\yjcomment{I still feel we should give a reason why we choose UD. One
  example is that twitter users tend to leave out the copula verb and
  it will be messy for the `function head' principle to deal with this
  case. One observation is that informal tokens/syntax happens more on
  function words rather than content word.} \nascomment{maybe we could
  argue that, if UD is designed to work for many languages, it should
  also be able to work for dialects, including AAVE, and informal
  registers.  YM was not designed for cross-linguistic applicability.}

\end{itemize}

Contribution of this paper includes:
\begin{itemize}
\item We create a new annotated tweet dependency treebank ({\sc Tweebank v2}) following the UD convention.
This annotation contains 3,549 tweets.
Tokenization, part-of-speech tag, and dependencies of these tweets are annotated in this data.

\item We propose to use the transition-based neural parser \cite{ballesteros-EtAl:2016:EMNLP2016} with consideration of the speed in processing social media data.
To achieve a more accurate parser, we propose to train the parser with a distillation of an ensemble 20 parser and this achieve an improvement of 3 point LAS over the baseline.
\end{itemize}

We release our parser at.

\nascomment{not clear to me:  did we reannotate the POS corpus?  was
  that automatic or manual?  I wasn't sure what to do with the POS
  section below.}

\section{Annotation}

@@

Another important difference is in tokenization.  UD calls for more
aggressive tokenization than that used by
\newcite{gimpel-EtAl:2011:ACL-HLT2011}, which followed
\newcite{oconnor-2010}.  In particular, they opted out of tokenizing
contractions and possessives, introducing new parts of speech
instead.\footnote{These tags only accounted for 2.7\% of tokens,
  leading to concerns about data sparseness in tagging and all
  downstream analyses.}  For us, these tokens must be split, but
universal parts of speech can be applied.

@@

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{rc}
		\hline
		\it System & F \\
		\hline
		Stanford Tokenizer & 96.6 \\
		Twokenizer & 94.4 \\
		UD pipe v1.2 & 94.7 \\
		UD pipe v1.2 (re-trained) & 97.3 \\
		Our Tokenizer & \bf 98.3 \\
		\hline
	\end{tabular}
	\caption{The tokenization result.}\label{tbl:tok-result}
\end{table}

@@

%Our experimental results show that
\subsection{POS-Tagger}

We use the postagger of \newcite{owoputi-EtAl:2013:NAACL-HLT}.
%In our preliminary experiments, neural model didn't show superiority over the rich-feature linear model.

@@

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{rc}
		\hline
		\it System & P \\
		\hline
		Stanford Postagger & 65.6 \\
		Stanford Postagger (re-train) & 90.37 \\
		UD pipe v1.2 & 78.7 \\
		UD pipe v1.2 (re-trained) & 83.8 \\
		Our bi-LSTM & 91.8 \\
		\newcite{owoputi-EtAl:2013:NAACL-HLT} & \bf 95.1 \\
		\hline
	\end{tabular}
	\caption{The POS tagging result on gold tokenization.}\label{tbl:pos-result}
\end{table}

@@

We show the effect of $\alpha$ in Figure \ref{fig:effect-alpha}.
This figure shows that a larger $\alpha$

@@

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{rcc}
		\hline
		\it System & UAS & LAS \\
		\hline
		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 79.25 & 74.17 \\
		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & & \\
		Ensemble 20 & 82.80 & 78.69 \\
		Distill & & \\

		\hline
	\end{tabular}
	\caption{The POS tagging result.}\label{tbl:parse-result}
\end{table}

>>>>

\newcommand{\yjcomment}[1]{\textcolor{orange}{[$_\mathrm{L}^\mathrm{Y}$#1]}}
\newcommand{\nascomment}[1]{\textcolor{blue}{[#1 ---\textsc{nas}]}}

@@

\section{Introduction}
Analyzing the syntax of tweets is challenging. The challenges not
only come from the difficulty of adapting the parser trained on the
standard text to the Twitter domain, but also comes from creating
reasonable dataset for training and evaluating tweet parsers. 
\citet{AAAIW113912} pioneered in this research direction by
annotating Penn Treebank \citep[PTB]{Marcus93buildinga}
constituencies to a set of tweets which contains 7,630 tokens. 
Stanford dependencies were converted afterwards. 
\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
annotating tweets and presented a tweets treebank ({\sc Tweebank})
which has 12,149 tokens and was created using the 
\citet{Yamada03statisticaldependency} dependencies. Both these
annotation efforts were highly influenced by the PTB whose guideline
has a good grammatical coverage on newswire. However, when it comes
to the noisy and informal user generated text, it's questionable
whether such good coverage holds.
%Motivation notes:  explain why UD is attractive (and more attractive
%than what previous work used, which was based on YM).  one reason is
%that it might allow sharing of texts annotated in different genres (or
%even languages, cite Waleed).  but universal annotation schemes are
%challenging!  this paper contends with the challenges of
%applying UD to social media texts.

%In this paper, we propose to parse the tweets in the convention of
%universal dependencies and built up the whole pipeline to parse the
%tweets from the raw text form.

Universal dependencies \citep[UD]{NIVRE16.348} was created to delivery
consistent annotation across different languages. To allow such
consistency, UD was designed to be adaptive to different genres and languages
\cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. It's promising that analyzing
the syntax of tweets can benefit from such adaptability. In this paper,
we create a new tweets treebank of 55,607 tokens by following the UD
guidelines but also contending the domain-specific challenges which wasn't
covered by UD guidelines. Our annotation includes a whole pipeline of
tokenization, part-of-speech (POS) tags and universal dependencies.

%\nascomment{Points that were in older text that I want to keep around:}
%\begin{itemize}
%\item Despite the informal nature of tweets, we argue that they basically follow the same grammar as their formal language counterpart.
%\item UD was designed to handle the variant syntactic phenomenons across different languages and we expect its `context head' principle will bring convenience to the parsing of informal and even ungrammatical tweets. 
%\yjcomment{I still feel we should give a reason why we choose UD. One
%  example is that twitter users tend to leave out the copula verb and
%  it will be messy for the `function head' principle to deal with this
%  case. One observation is that informal tokens/syntax happens more on
%  function words rather than content word.} \nascomment{maybe we could
%  argue that, if UD is designed to work for many languages, it should
%  also be able to work for dialects, including AAVE, and informal
%  registers.  YM was not designed for cross-linguistic applicability.}
%\end{itemize}

Based on these annotations, we built up a whole pipeline to parse the
raw tweet text into universal dependencies. Our pipeline includes: a
bidirectional LSTM (bi-LSTM) tokenizer, a word cluster enhanced POS
tagger \cite{owoputi-EtAl:2013:NAACL-HLT}, and stack-lstm parser
with character representation \cite{ballesteros-dyer-smith:2015:EMNLP}.

To achieve better performance without sacrificing efficiency, we propose
a new method to train the parser with the distillation 
\cite{DBLP:journals/corr/HintonVD15} of 20 parsers ensemble.
We show that learning from the exploration of the ensemble parser
can be more beneficial than just learning from the gold standard
transition sequence in the sense of training a transition-based
distilling parser. Experimental results show an improvement of more
than 3 points in LAS over baseline parser can be achieved with our
distillation method.

Contribution of this paper includes:
\begin{itemize}
\item We study the challenges of annotating tweets in UD (\S\ref{sec:anno})
and create a new tweet treebank ({\sc Tweebank v2}), which includes 
tokenization, part-of-speech tagging, and dependencies annotation.

\item We built up a whole pipeline to parse the raw tweet text into
universal dependencies (\S\ref{sec:parsing}). We propose a new distillation
method in training the parser in our pipeline which achieve 3 points improvement
without sacrificing efficiency.
\end{itemize}

We release our system at.

\nascomment{not clear to me:  did we reannotate the POS corpus?  was
  that automatic or manual?  I wasn't sure what to do with the POS
  section below.}
\yjcomment{we re-annotated the POS. In one way, Gimple's POS is not very
consistent with UD POS. In another way, 2,500 new tweets were annotated
from scratch and they didn't have Gimple's tags.}

\section{Annotation}\label{sec:anno}

@@

Another important difference is in tokenization.  UD calls for more
aggressive tokenization than that used by
\newcite{gimpel-EtAl:2011:ACL-HLT2011}, which followed
\newcite{ICWSM101540}.  In particular, they opted out of tokenizing
contractions and possessives, introducing new parts of speech
instead.\footnote{These tags only accounted for 2.7\% of tokens,
  leading to concerns about data sparseness in tagging and all
  downstream analyses.}  For us, these tokens must be split, but
universal parts of speech can be applied.

@@

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{rc}
		\hline
		\it System & F \\
		\hline
		Stanford Tokenizer & 96.6 \\
		Twokenizer & 94.4 \\
		UD pipe v1.2 & 94.7 \\
		UD pipe v1.2 (re-trained) & 97.3 \\
		Our Tokenizer & \bf 98.3 \\
		\hline
	\end{tabular}
	\caption{The tokenization results.}\label{tbl:tok-result}
\end{table}

@@

\subsection{POS-Tagger}

Part-of-Speech tagging for tweets has been studied in previous literals \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
We use the postagger of \newcite{owoputi-EtAl:2013:NAACL-HLT}.

@@

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{rc}
		\hline
		\it System & P \\
		\hline
		Stanford Postagger & 65.6 \\
		Stanford Postagger (re-train) & 90.4 \\
		UD pipe v1.2 & 78.7 \\
		UD pipe v1.2 (re-trained) & 83.8 \\
		bi-LSTM & 91.8 \\
		ARK Tagger & \bf 95.1 \\
		\hline
	\end{tabular}
	\caption{The POS tagging result on gold tokenization.}\label{tbl:pos-result}
\end{table}

@@

We show the effect of $\alpha$ in Figure \ref{fig:effect-alpha}.
This figure shows that parsers with larger $\alpha$ achieves better performance than that with smaller $\alpha$.
This result shows that learning from the hard target in unnecessary.

@@

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{rcc}
		\hline
		\it System & UAS & LAS \\
		\hline
		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 79.25 & 74.17 \\
		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.90 & 72.95 \\
		Ensemble 20 & 82.80 & 78.69 \\
		Distill expert ($\alpha$=0.)& 81.22 & 76.98 \\
		Distill boltzmann ($\mathcal{T}$=1) & 81.55 & 77.32 \\
		\hline
	\end{tabular}
	\caption{The POS tagging result.}\label{tbl:parse-result}
\end{table}
